---
title: ":package: SMRD: Statistical Methods for Reliability Data"
author: "Jason K. Freels, William Q. Meeker, and Luis A. Escobar"
date: "<br/>`r format(Sys.Date(), '%d %B %Y')`"
output: 
  github_document:
    html_preview: false
keep_md: yes
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(SMRD)
```
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/SMRD)](https://cran.r-project.org/package=SMRD)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/Auburngrads/SMRD?branch=master&svg=true)](https://ci.appveyor.com/project/Auburngrads/SMRD)
  [![Travis build status](https://travis-ci.org/Auburngrads/SMRD.svg?branch=master)](https://travis-ci.org/Auburngrads/SMRD)
   [![Codecov test coverage](https://codecov.io/gh/Auburngrads/SMRD/branch/master/graph/badge.svg)](https://codecov.io/gh/Auburngrads/SMRD?branch=master)

## Background

Since its initial publication, <a target=' 'href='https://www.amazon.com/Statistical-Methods-Reliability-William-Meeker/dp/0471143286'>**Statistical Methods for Reliability Data**</a> has remained a foundational text for analyzing time-to-failure (survival) data.  Along with the first edition of the text, the authors provided an S-Plus software package, called [**SPLIDA**](http://www.public.iastate.edu/~splida/')  (**S**-**P**lus **LI**fe **D**ata **A**nalysis), to help readers utilize the methods for industry data.  

Today, R has supplanted S and S-Plus as the most popular statistical computing language in the world.  In response to this shift, Meeker began an effort to translate **SPLIDA** into R under the name **RSplida**. However, RSplida couldn't be installed as a traditional R package and was difficult to use with modern IDE's.  In 2015, Freels partnered with Meeker to restructure and modernize RSplida into this R package **SMRD**, with the aim of publishing to the <a target="" href="https://cran.r-project.org">**CRAN**</a>.

## Installation

As this package has not yet been published, you can install the latest development version from GitHub:

```{r, eval=FALSE}
if (packageVersion("devtools") < 1.6) {
  
    install.packages("devtools")
  
}

devtools::install_github("Auburngrads/SMRD")
```

Please note that this package is currently experimental and is under very active development.  If you encounter any problems or unexpected behaviours, please create a <a target="" href="https://github.com/Auburngrads/SMRD/issues">**new issue**</a> and include a reporducible example.

## Getting started 

Once installed, the easiest way get started using `SMRD` is by checking out the echapters.  These are documents that present example code and results that correspond to what is shown in the each chapter of the 1st edition of the SMRD text.

```{r, eval=FALSE}
SMRD::echapter(chapter = 1)
```

## Getting involved

There are a number of tasks that need to be completed before publishing. These issues can be broken down into four main project areas.  The links below show the current issues that exist within these areas.

- <a target="" href="https://github.com/Auburngrads/SMRD/projects/1">**Update graphics objects**</a>
- <a target="" href="https://github.com/Auburngrads/SMRD/projects/4">**Document datasets and functions**</a>
- <a target="" href="https://github.com/Auburngrads/SMRD/projects/2">**Update for modern use-cases - literate programming/interactivity**</a>
- <a target="" href="https://github.com/Auburngrads/SMRD/projects/3">**Improve/update implementation of statistical methods**</a>
