---
title: "`r SMRD:::info('book')`"
subtitle: "`r SMRD:::info('chapter15')`"
author: "`r SMRD:::info('authors')`"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    css: my-vignette.css
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{echapter15}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
SMRD:::vinny()
library(SMRD)
```

# In This Vignette...

component.effect(parallel = TRUE)

parallel.effect()

parallel.dep.effect()

series.dep.effect()

Create the `life.data` object and print the data summary

```{r}
DeviceG.ld <- frame.to.ld(deviceg,
                          response.column = 1, 
                          failure.mode.column =  2)

summary(DeviceG.ld)
```

Provide basic plots

```{r}
event.plot(DeviceG.ld)
```

```{r}
par(mfrow = c(1,2))
plot(DeviceG.ld, distribution = "weibull")
plot(DeviceG.ld, distribution = "lognormal")
par(mfrow = c(1,1))
```

summary(ld.to.mfld(DeviceG.ld))

# Plots the individual failure modes separately

```{r}
par(mfrow = c(1,2))
mfmi.mleprobplot(DeviceG.ld, distribution = "weibull") 
mfmi.mleprobplot(DeviceG.ld, distribution = "lognormal") 
par(mfrow = c(1,1))
```

# Plots both modes in one plot

```{r}
mfmc.mleprobplot(DeviceG.ld, 
                 distribution = "Weibull") 

mfmc.mleprobplot(DeviceG.ld, 
                 distribution = "Weibull", 
                 band.type = "none")

tmp <- mfmc.mleprobplot(DeviceG.ld, 
                       distribution = "Weibull", 
                       band.type = "none", 
                       show.individual = F, 
                       ylim = c(0.1, .99))
failure.probabilities(tmp)
quantiles(tmp)
```

# different distributions for the different failure modes

```{r}
tmpx <- mfmc.mleprobplot(DeviceG.ld, 
                         distribution = "Weibull", 
                         distribution.vec = c("Weibull","Lognormal"))

failure.probabilities(tmpx)
quantiles(tmpx)
```

mfm.to.ld(DeviceG.ld)

#	Shock Absorber Data

```{r}
ShockAbsorber.ld <- frame.to.ld(shockabsorber,
                                response.column = 1,
                                failure.mode.column = 2,
                                censor.column = 3, 
                                time.units = "Kilometers")
summary(ShockAbsorber.ld)
event.plot(ShockAbsorber.ld)
```

## Split out by failure mode

```{r}
mleprobplot(ShockAbsorber.ld, 
            distribution = "Weibull")

mfmi.mleprobplot(ShockAbsorber.ld, 
                 distribution = "Weibull")

tmpx <- mfmc.mleprobplot(ShockAbsorber.ld, 
                         distribution = "Weibull")

failure.probabilities(tmpx)
quantiles(tmpx)
```

```{r}

ShockAbsorber.mfld <- mfm.to.ld(ShockAbsorber.ld)

multiple.mleprobplot(ShockAbsorber.mfld,
                     data.ld.name="xx",
                     xlab="yy",
                     distribution="Weibull")

mleprobplot(ShockAbsorber.Mode1.ld, 
            distribution = "Weibull")

mleprobplot(ShockAbsorber.Mode2.ld,
            distribution = "Weibull")

get.time.vector(ShockAbsorber.Mode2.ld)
```

#	connection strength data

```{r}
ConnectionStrength.ld <- 
  frame.to.ld(connectionstrength,
              response.column = 1,
              failure.mode.column = 2,
              case.weight.column = 3)

summary(ConnectionStrength.ld )
event.plot(ConnectionStrength.ld)

mfm.to.ld(ConnectionStrength.ld)

mleprobplot(ConnectionStrength.Bond.ld , 
            distribution = "normal")

mlest(ConnectionStrength.Bond.ld , 
      distribution = "normal")
```


# the following causes R to crash---using genmax

```{r, eval=FALSE}
gmlest(ConnectionStrength.Bond.ld , 
       distribution = "normal")
```

```{r}
mfmi.mleprobplot(ConnectionStrength.ld,
                 distribution = "Normal")

tpmx <- mfmc.mleprobplot(ConnectionStrength.ld,
                         distribution = "Normal")

failure.probabilities(tmpx)
quantiles(tmpx)
```

