---
title: "`r SMRD:::info('book')`"
subtitle: "`r SMRD:::info('chapter8')`"
author: "`r SMRD:::info('authors')`"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    css: my-vignette.css
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{echapter8}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
SMRD:::vinny()
library(SMRD)
```

# Shockabsorber Data Set - Both Failure Modes

```{r}
ShockAbsorber.ld <- frame.to.ld(shockabsorber,
                                response.column = 1, 
                                censor.column = 3,
                                time.units = "Kilometers")
```

## Create an `mleprobplot` array

```{r, fig.height=12, echo=2:5, fig.width=8}
par(mfrow = c(2,2))
mleprobplot(ShockAbsorber.ld, distribution="Weibull")
mleprobplot(ShockAbsorber.ld, distribution = "loglogistic")
mleprobplot(ShockAbsorber.ld, distribution = "lognormal")
mleprobplot(ShockAbsorber.ld, distribution = "frechet")
par(mfrow = c(1,1))
```

## Create an `mleprobplot` array

```{r, fig.height=12, fig.width=8}
four.mleprobplot(ShockAbsorber.ld)
```

## Create an `mlest` object

```{r}
ShockAbsorber.mlest <- mlest(ShockAbsorber.ld, 
                             distribution = "Weibull")
print(ShockAbsorber.mlest)$ll.text
print(ShockAbsorber.mlest)$mttf.text
print(ShockAbsorber.mlest)$mle.table
print(ShockAbsorber.mlest)$vcv.matrix
print(ShockAbsorber.mlest)$param.corr.matrix
print(ShockAbsorber.mlest)$failure.probabilities
print(ShockAbsorber.mlest)$quantiles
```

# Create Contour Plots

- Plot Two and Three-dimensional confidence contours 
<div class="columns-2">
```{r, echo=1:9}
simple.contour(ShockAbsorber.ld,
               distribution = "lognormal",
               show.confidence = T)


simple.contour(ShockAbsorber.ld,
               distribution = "lognormal",
               show.confidence = T,
               threeD = T)
```
</div>

simple.contour(ShockAbsorber.ld,"lognormal",show.confidence = F)
simple.contour(ShockAbsorber.ld,"lognormal",threeD = T)
simple.contour(ShockAbsorber.ld,"lognormal",quantile=.1)
simple.contour(ShockAbsorber.ld,"lognormal",quantile=.3)
simple.contour(ShockAbsorber.ld,"lognormal",quantile=.3,log.quantile=T)
simple.contour(ShockAbsorber.ld,"lognormal",quantile=.3,rel.or.conf="")
simple.contour(ShockAbsorber.ld,"lognormal",quantile = .3,threeD = T)


failure.probabilities(ShockAbsorber.mlest,time.vec=seq(5000, 50000, by=2500), digits=13)



#compare lognormal and Weibull
compare.mleprobplot(ShockAbsorber.ld, 
                    main.distribution= "Lognormal",
                    compare.distribution="Weibull")


#plot of hazard function

mlehazplot(ShockAbsorber.ld, 
           distribution="Weibull", 
           param.loc = "topleft")

mlehazplot(ShockAbsorber.ld, 
           distribution="Frechet")


mlehazplot(ShockAbsorber.ld, 
           distribution="Lognormal")


mlehazplot(ShockAbsorber.ld, 
           distribution="Lognormal",
           xlim=c(5000,500000), y.axis="log")


mlehazplot(ShockAbsorber.ld, 
           distribution = "Weibull",
           time.vec = c(10000,20000,30000))

mlehazplot(ShockAbsorber.ld, 
           distribution = "Weibull",
           time.vec = c(10000,20000,30000),
           parameter.fixed = c(F,T),
           theta.start = c(9.,2))


# Bearing Cage Data Set

BearingCage.ld <- frame.to.ld(bearingcage,
                              response.column = 1, 
                              censor.column = 2, 
                              case.weight.column = 3,
                              time.units = "Hours")

summary(BearingCage.ld)


mleprobplot(BearingCage.ld, distribution = "Weibull")

mleprobplot(BearingCage.ld, 
            distribution="Weibull", 
            parameter.fixed=c(F,T),
            theta.start=c(2,.6667),
            sub.title="sigma = .667  (or beta = 1.5)")

mleprobplot(BearingCage.ld, 
            distribution="Weibull", 
            parameter.fixed=c(F,T),
            theta.start=c(9.,.5),
            sub.title="sigma = .5  (or beta = 2)")

mleprobplot(BearingCage.ld, 
            distribution="Weibull", 
            parameter.fixed=c(F,T),
            theta.start=c(9.,.3333),
            sub.title="sigma = .333  (or beta = 3)")

tmpgmle.out <- ls2.mle(BearingCage.ld, 
                       distribution ="Weibull", 
                       theta.start=c(9,.4))

simple.contour(BearingCage.ld,
               distribution = "Weibull",
               zoom.level = 4,
               quantile = .1,
               threeD = TRUE)

simple.contour(BearingCage.ld,
               distribution = "Weibull",
               zoom.level = 4,
               profile = "x")

simple.contour(BearingCage.ld,
               distribution = "Weibull",
               zoom.level = 4,
               profile = "y")


simple.contour(BearingCage.ld,
               distribution = "Weibull",
               threeD = T,
               zoom.level = 3,
               size = 75)

simple.contour(ShockAbsorber.ld,"Weibull", zoom.level = 3)
simple.contour(ShockAbsorber.ld,"Weibull", threeD=T)
tmp <- simple.contour(ShockAbsorber.ld,"Weibull", zoom.level = 3, size = 50)

#
#the following requires interaction
#
#       newspinp(tmp)


# examples of use of compare.mleprobplot

compare.mleprobplot(ShockAbsorber.ld, main.distribution= "Lognormal",compare.distribution="Weibull")

compare.mleprobplot(BearingCage.ld,main.distribution= "Lognormal",compare.distribution="Weibull",xlim=c(201,9900),ylim=c(.0001,.5),time.range = c(201,9900))


compare.mleprobplot(ShockAbsorber.ld, main.distribution= "Lognormal",compare.distribution=c("Weibull","Loglogistic"))

compare.mleprobplot(ShockAbsorber.ld, main.distribution= "Lognormal",xlim=c(100,100000),ylim=c(.005,.9),compare.distribution=c("Weibull","Loglogistic"))

compare.mleprobplot(ShockAbsorber.ld, main.distribution= "Lognormal",xlim=c(100,50001),ylim=c(.005,.9),compare.distribution=c("Weibull","Loglogistic","Exponential"),band.type="chull")

compare.mleprobplot(ShockAbsorber.ld, main.distribution= "Lognormal",xlim=c(100,100000),ylim=c(.005,.9),compare.distribution=c("Weibull","Exponential"),band.type="chull")





bulb.ld <- frame.to.ld(bulb,
                       response.column = 1,
                       data.title = "Bulb Data",
                       time.units = "Hours")

mlest(bulb.ld,"lognormal")

simple.contour(bulb.ld,"lognormal", quantile = .5)



#
#Here are some examples of the "simple" contours and profiles using lower-level functions
#
#
#Here we have the eta parameter on the x axis
#
ShockAbsorber.likelihood.grid.out <- simple.grid(data.ld=ShockAbsorber.ld,distribution="Weibull")
plot.simple.contour(contour.indicators=c(.001,.01,.1,.5,.9),do.persp=F,rel.or.conf="Relative Likelihood",likelihood.grid.out=ShockAbsorber.likelihood.grid.out)
profile.plot(profile.grid(ShockAbsorber.likelihood.grid.out, which = "x"))
profile.plot(profile.grid(ShockAbsorber.likelihood.grid.out, which = "y"))
profile.plot(profile.grid(ShockAbsorber.likelihood.grid.out, which = "y"),log.axis=TRUE)



#
#Here we have the 0.1 quantile on the x axis
#
ShockAbsorber.likelihood.grid.out <- simple.grid(data.ld=ShockAbsorber.ld,distribution="Weibull",the.quantile=0.1)
plot.simple.contour(contour.indicators=c(50., 95.),do.persp=T,rel.or.conf="Joint confidence region",the.quantile=0.1,likelihood.grid.out=ShockAbsorber.likelihood.grid.out)
plot.simple.contour(contour.indicators=c(50., 95.),do.persp=F,rel.or.conf="Joint confidence region",the.quantile=0.1,likelihood.grid.out=ShockAbsorber.likelihood.grid.out)
plot.simple.contour(contour.indicators=c(.001,.01,.1,.5,.9),do.persp=F,rel.or.conf="Relative Likelihood",the.quantile=0.1,likelihood.grid.out=ShockAbsorber.likelihood.grid.out)
profile.plot(profile.grid(ShockAbsorber.likelihood.grid.out, which = "x"))
profile.plot(profile.grid(ShockAbsorber.likelihood.grid.out, which = "y"))

plot.simple.contour(contour.indicators=c(50., 95.),do.persp=TRUE,rel.or.conf="Joint confidence region",the.quantile=0.1,likelihood.grid.out=ShockAbsorber.likelihood.grid.out)


#
#The "brute-force" profileing code below needs a little more work to get it working 100% again.
#  The profiling is done on the "stable parameters" used in estimation
#   These codes are rather general, but were designed to do the figures in the book.
#   They were never optimized for user-friendlyness
#    two.dim.profile and one.dim.profile compute (possibly using a lot of computer time)
#    and  the profiles and automatically creates an object
#    Then there the folowing commands are used to make the plot(s).
#

ShockAbsorber.weibull.gmle.out <- ls.mle(ShockAbsorber.ld, distribution = "Weibull")


#short test
two.dim.profile(ShockAbsorber.weibull.gmle.out, profile.on.list = NULL,which=c(1,2), size = c(2,2), range.list = list(c(9.0,10.4),c(-1.8,-.1)),monitor=1)


two.dim.profile(ShockAbsorber.weibull.gmle.out, profile.on.list = NULL,which=c(1,2),size = c(25,25), range.list = list(c(9.0,10.4),c(-1.8,-.1)))



profile.contour(ShockAbsorber.weibull.gmle.outstruct1x2,variable.namey="log(sigma)")

conf.contour(ShockAbsorber.weibull.gmle.outstruct1x2,transformationy="log",variable.namey="log(sigma)" )



#short test
one.dim.profile(ShockAbsorber.weibull.gmle.out,size = 2, range.list = list(c(9.0,10.2),c(-1.8,-.4)))


one.dim.profile(ShockAbsorber.weibull.gmle.out,size = 200, range.list = list(c(9.8,10.8),c(-1.8,-.4)))


profile.plot(ShockAbsorber.weibull.gmle.outstruct1)

profile.plot(transtruct(ShockAbsorber.weibull.gmle.outstruct1,exp),variable.name="eta")

profile.plot(ShockAbsorber.weibull.gmle.outstruct2)

profile.plot(transtruct(ShockAbsorber.weibull.gmle.outstruct2,exp),variable.name="sigma")


#define the transformation on the fly to get beta=exp(-log(sigma))
profile.plot(transtruct(ShockAbsorber.weibull.gmle.outstruct2,function(x){exp(-x)}),variable.name="beta")

#short test
two.dim.profile(ShockAbsorber.weibull.gmle.out, profile.on.list = NULL,which=c(5,3), special.stuff.profile=list(spec.quantile=.1),profile.setup=quantile.profile.setup, profile.stable.parameters = quantile.profile.stable.parameters,size = c(4,4), range.list =list(c(9.8,10.8),c(-1.8,-.4),c(.165,.670),NULL,c(5000,20000)))

two.dim.profile(ShockAbsorber.weibull.gmle.out, profile.on.list = NULL,which=c(5,3), special.stuff.profile=list(spec.quantile=.1),profile.setup=quantile.profile.setup, profile.stable.parameters = quantile.profile.stable.parameters,size = c(20,20), range.list =list(c(9.8,10.8),c(-1.8,-.4),c(.165,.670),NULL,c(5000,20000)))




profile.contour(ShockAbsorber.weibull.gmle.outstruct5x3,variable.namex="t_.01",variable.namey="sigma",levels = c(0.01, .1,0.2, 0.4, 0.7, 0.9) )

conf.contour(ShockAbsorber.weibull.gmle.outstruct5x3,levels = c(50,90,99))


 one.dim.profile(ShockAbsorber.weibull.gmle.out, profile.on.list = 5,special.stuff.profile = list(spec.quantile = .1), size = 200, profile.setup = quantile.profile.setup,profile.stable.parameters = quantile.profile.stable.parameters, range.list = list(c(5000,20000)),addname="t.1")

 one.dim.profile(ShockAbsorber.weibull.gmle.out, profile.on.list = 5,special.stuff.profile = list(spec.quantile = .632), size = 200, profile.setup = quantile.profile.setup,profile.stable.parameters = quantile.profile.stable.parameters, range.list = list(c(5000,20000)),addname="eta")


profile.plot(ShockAbsorber.weibull.gmle.outstruct5t.1)


 one.dim.profile(ShockAbsorber.weibull.gmle.out, profile.on.list = 6,special.stuff.profile = list(spec.time=10000), size = 200, profile.setup = quantile.profile.setup, profile.stable.parameters = quantile.profile.stable.parameters,range.list = list(c(.001,.2)),addname="F10k")


profile.plot(ShockAbsorber.weibull.gmle.outstruct6F10k)


 one.dim.profile(ShockAbsorber.weibull.gmle.out, profile.on.list = 6, special.stuff.profile = list(spec.time=20000), size = 200, profile.setup = quantile.profile.setup, profile.stable.parameters = quantile.profile.stable.parameters, range.list = list(c(.12,.5)),addname="F20k")


profile.plot(ShockAbsorber.weibull.gmle.outstruct6F20k)
