---
title: "`r SMRD2:::info('book')`"
subtitle: "`r SMRD2:::info('chapter16')`"
author: "`r SMRD2:::info('authors')`"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    css: my-vignette.css
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{echapter16}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
SMRD2:::vinny()
library(SMRD2)
```

## Chapter Overview

###	workstation reboots

```{r workstation}
#time.column, ID.column, cost.count.column, event.column
WorkStation.rdu <- SMRD2:::frame.to.rdu(workstation,
                                ID.column = "station",
                                time.column = "days",
                                event.column = "event")

#attr(WorkStation.rdu,"WindowInfo")

WorkStation.mcf <- SMRD2:::mcf(WorkStation.rdu)

#sqrt(WorkStation.mcf$Var)

event.plot(WorkStation.rdu)

plot(WorkStation.mcf)
```

##	computer Lab data

```{r computerlab}
ComputerLab.rdu <- frame.to.rdu(computerlab,
                                ID.column = "computer",
                                time.column = "days",
                                event.column = "event")

#attr(ComputerLab.rdu,"WindowInfo")

ComputerLab.mcf <- mcf(ComputerLab.rdu)

#sqrt(ComputerLab.mcf$Var)

event.plot(ComputerLab.rdu)

plot(ComputerLab.mcf)
```

##	locomotive valveseat replacements

```{r valveseat}
ValveSeat.rdu <- frame.to.rdu(valveseat,
                              ID.column = "engine", 
                              time.column = "days" ,
                              event.column = "event", 
                              data.title = "Valve-Seat Replacement Data",
                              time.units = "Days")

#attr(ValveSeat.rdu,"WindowInfo")

summary(ValveSeat.rdu)

event.plot(ValveSeat.rdu)

SMRD2:::mcf.plot(ValveSeat.rdu)
```

##	locomotive Cylinder replacements

```{r cylinder}
Cylinder.rdu <- frame.to.rdu(cylinder,
                             ID.column = "engine", 
                             time.column = "days", 
                             event.column = "event", 
                             cost.count.column = "count", 
                             data.title = "Cylinder Replacement Data",
                             time.units = "Days")

#attr(Cylinder.rdu,"WindowInfo")

PlotMCFandNHPP(Cylinder.rdu, form = "power rule")

Cylinder.mcf <- mcf(Cylinder.rdu)

plot(Cylinder.mcf)
```

##	Locomotive Grids1 replacements

```{r grids1}
Grids1.rdu <- frame.to.rdu(grids1,
                           ID.column = "unit", 
                           time.column = "days",
                           event.column = "event",
                           data.title = "Grids1 Replacement Data",
                           time.units = "Days")

summary(Grids1.rdu)

event.plot(Grids1.rdu)
print(mcf(Grids1.rdu))
mcf.plot(Grids1.rdu)

#attr(Grids1.rdu,"WindowInfo")

PlotMCFandNHPP(Grids1.rdu, form = "power rule")
Grids1.mcf <- mcf(Grids1.rdu)
plot(Grids1.mcf)
```

##	Locomotive Grids2 replacements

```{r grids2}
Grids2.rdu <- frame.to.rdu(grids2, 
                           time.column = c(2), 
                           event.column = 3,
                           ID.column = 1, 
                           data.title = "Grids2 Replacement Data",
                           time.units ="Days")

summary(Grids2.rdu)

#attr(Grids2.rdu,"WindowInfo")

PlotMCFandNHPP(Grids2.rdu,
               form = "power rule")
Grids2.mcf <- mcf(Grids2.rdu)
plot(Grids2.mcf)

event.plot(Grids2.rdu)
print(mcf(Grids2.rdu))
mcf.plot(Grids2.rdu)

mcf.diff.plot(Grids1.rdu,
              Grids2.rdu,
              plot.seg = T,
              xlab = "Locomotive Age in Days",
              ylab = "Difference in Mean Cumulative Replacements")
```

##	Halfbeak

```{r halfbeak}
halfbeak.rdu <- frame.to.rdu(halfbeak,
                             ID.column = "unit", 
                             time.column = "hours" ,
                             event.column = "event", 
                             data.title = "Halfbeak Data", 
                             time.units = "Thousands of Hours of Operation")

summary(halfbeak.rdu)
event.plot(halfbeak.rdu)
print(mcf(halfbeak.rdu))
mcf.plot(halfbeak.rdu)
interarrival.times(halfbeak.rdu)
mcf.plot(halfbeak.rdu,
         xlab = "Thousands of Hours of Operation",
         ylab = "Cumulative Number of Maintenance Actions")
```

## Halfbeak additional plots

```{r halfbeak2}
interarrival.plot(halfbeak.rdu,
                  xlab = "Thousands of Hours of Operation",
                  ylab = "Thousands of Hours Between Maintenance Actions",
                  my.title="")

ar1.plot(halfbeak.rdu,
         xlab = "Lagged Thousands of Hours Between Maintenance Actions",
         ylab = "Thousands of Hours Between Maintenance Actions")

ar1.plot(halfbeak.rdu,
         xlab = "Lagged Thousands of Hours Between Maintenance Actions",
         ylab = "Thousands of Hours Between Maintenance Actions",
         plot.acf = T)

fit.power.and.loglin.process(halfbeak.rdu,
                             xlab = "Thousands of Hours of Operation",
                             ylab = "Cumulative Number of Maintenance Actions")
legend(SMRD:::x.loc(.01),
       SMRD:::y.loc(.95),
       legend = c("Nonparametric MCF estimate",
                  "Log-linear Recurrence Rate NHPP MCF",
                  "Power Recurrence Rate NHPP MCF"),
       lty=c(1,1,3),
       lwd=c(3,1,1))


repair.tsplot(halfbeak.rdu)
interarrival.plot(halfbeak.rdu)
ar1.plot(halfbeak.rdu)

renewal.plots(halfbeak.rdu)
laplace.test(halfbeak.rdu)
lewis.robinson.test(halfbeak.rdu)
milhbk189.test(halfbeak.rdu)

PlotMCFandNHPP(halfbeak.rdu, form = "power rule")
PlotMCFandNHPP(halfbeak.rdu, form = "log linear")
```

### fit.power.process(halfbeak.rdu)
### fit.loglin.process(halfbeak.rdu)
fit.power.and.loglin.process(halfbeak.rdu)

TestWindow(halfbeak[[1]],halfbeak[[2]],halfbeak[[3]],NULL)
event.plot(halfbeak.rdu )
attr(halfbeak.rdu,"WindowInfo")


TestWindow(halfbeak[[1]],halfbeak[[2]],halfbeak[[3]],NULL)

RiskSet(halfbeak.rdu )


halfbeak.mcf.out <- mcf(halfbeak.rdu)
plot(halfbeak.mcf.out )
fit.power.and.loglin.process(halfbeak.rdu)

NHPP.mle(halfbeak.rdu,form="power rule")
NHPP.mle(halfbeak.rdu,form="log linear")

PlotMCFandNHPP(halfbeak.rdu,form="log linear")
PlotMCFandNHPP(halfbeak.rdu,form="power rule")

##	Grampus

```{r grampus}
grampus.rdu <- frame.to.rdu(grampus, 
                            time.column = c(2), 
                            event.column = 3,
                            data.title = "Grampus Data", 
                            ID.column = 1, 
                            time.units ="Thousands of Hours of Operation")

summary(grampus.rdu)

event.plot(grampus.rdu)
print(mcf(grampus.rdu))

mcf(grampus.rdu)

mcf.plot(grampus.rdu)

interarrival.times(grampus.rdu)
repair.tsplot(grampus.rdu)
interarrival.plot(grampus.rdu)
ar1.plot(grampus.rdu)

renewal.plots(grampus.rdu)
milhbk189.test(grampus.rdu)
lewis.robinson.test(grampus.rdu)
laplace.test(grampus.rdu)

PlotMCFandNHPP(grampus.rdu,form="power rule")
PlotMCFandNHPP(grampus.rdu,form="log linear")

fit.power.and.loglin.process(grampus.rdu)
```

PlotMCFandNHPP(grampus.rdu,form=c("power rule","log linear"))

## fit weibull to times between failures

```{r grampus2}
mleprobplot(interarrival.times(grampus.rdu),"Weibull")

mcf.plot(grampus.rdu,
         xlab="Thousands of Hours of Operation",
         ylab="Cumulative Number of Maintenance Actions")

interarrival.plot(grampus.rdu,
                  xlab="Thousands of Hours of Operation",
                  ylab="Thousands of Hours Between Maintenance Actions",
                  my.title="")

ar1.plot(grampus.rdu,
         xlab="Lagged Thousands of Hours Between Maintenance Actions",
         ylab="Thousands of Hours Between Maintenance Actions",
         my.title="")

fit.power.and.loglin.process(grampus.rdu,
                             xlab = "Thousands of Hours of Operation",
                             ylab = "Cumulative Number of Maintenance Actions")
legend(SMRD:::x.loc(.02), 
       SMRD:::y.loc(.98),
       legend = c("Nonparametric MCF estimate",
                  "Log-linear Recurrence Rate NHPP MCF",
                  "Power Recurrence Rate NHPP MCF"),
       lty=c(1,1,3),
       lwd=c(3,1,1))

lewis.robinson.test(grampus.rdu)
```

##	Machine H Repair Labor Hours

```{r machineh}
MachineH.rdu <- frame.to.rdu(machineh,
                             ID.column = "unit", 
                             time.column = "hours",
                             event.column = "event", 
                             cost.count.column = "cost", 
                             data.title = "Earth-Moving Machine Repair Labor Hours", 
                             time.units = "Hours of Operation")

event.plot(MachineH.rdu,
           my.title = "", 
           xlab = "Hours of Operation", 
           which.system.to.plot = 1:23,
           ylab = "Machine Number")


mcf.plot(MachineH.rdu, 
         ylab = "Mean Cumulative Number of Labor Hours",
         plot.seg = T)

event.plot(MachineH.rdu)
attr(MachineH.rdu,"WindowInfo")

MachineH.mcf <- mcf(MachineH.rdu)
plot(MachineH.mcf)
PlotMCFandNHPP(MachineH.rdu, form = "power rule")
```

##	R4490 Labor Code Events

```{r r4490}
R4490.rdu <- frame.to.rdu(r4490,
                          ID.column = "vin",
                          time.column = "days" , 
                          cost.count.column = "costcount" ,
                          event.column = "code")

#attr(R4490.rdu,"WindowInfo")

event.plot(R4490.rdu)
#R4490.mcf <- mcf(R4490.rdu)
#plot(R4490.mcf)


#caused crash
if(FALSE){
R4490.nhpp.out <-PlotMCFandNHPP(R4490.rdu, form = "power rule")
one.dim.profile(R4490.nhpp.out,size = 5,save.s = T)
two.dim.profile(R4490.nhpp.out, 
                profile.on.list = NULL,
                which = c(1,2), 
                size = c(5,5))
profile.contour(R4490.nhpp.outstruct1x2,
                transformationy = "log",
                variable.namey = "sigma", 
                variable.namex = "mu", 
                v = c(0.001, 0.01, .1,0.2, 0.4, 0.7, 0.9) )
}
```

##	High Pressure Compressure Repairs

```{r hpcrepairs}
HPCRepairs.rdu <- frame.to.rdu(hpcrepairs,
                               ID.column = "system", 
                               time.column = "months" , 
                               event.column = "event")

attr(HPCRepairs.rdu,"WindowInfo")

PlotMCFandNHPP(HPCRepairs.rdu,form="power rule")
HPCRepairs.mcf <- mcf(HPCRepairs.rdu)
plot(HPCRepairs.mcf)
```

##	AMSAAExactFail

```{r amsaaexactfail, eval=FALSE}
SMRD2:::TestWindow(amsaaexactfail[[1]],
           amsaaexactfail[[2]],
           amsaaexactfail[[3]],
           NULL)

AMSAAExactFail.rdu <- frame.to.rdu(amsaaexactfail,
                                   ID.column = "vehicle", 
                                   time.column = "miles" , 
                                   event.column = "event")

names(attributes(AMSAAExactFail.rdu))

#
#testing the loglikelihood
#
theta.mat <- matrix(c(1,1,2,2),2,2)
theta.mat <- c(1,2)
#SMRD2:::loglikeNHPPvec(AMSAAExactFail.rdu, theta.mat, "power.law")
SMRD2:::TestLike(AMSAAExactFail.rdu, theta.mat, "power.law")

theta.mat <- matrix(c(.01,.01,.02,.02),2,2)
#SMRD2:::loglikeNHPPvec(AMSAAExactFail.rdu, theta.mat, "log.linear")

attr(AMSAAExactFail.rdu,"WindowInfo")

RiskSet(AMSAAExactFail.rdu)

plotRiskSet(AMSAAExactFail.rdu,proportion = T)

SMRD2:::get.UnitID(AMSAAExactFail.rdu)

mcf(AMSAAExactFail.rdu)

event.plot(AMSAAExactFail.rdu)

plotRiskSet(AMSAAExactFail.rdu,proportion = T)

plot(mcf(AMSAAExactFail.rdu))

PlotMCFandNHPP(AMSAAExactFail.rdu,
               form="log linear")

AMSAAExactFail.nhpp.out <- 
  PlotMCFandNHPP(AMSAAExactFail.rdu,
                 form="power rule")

one.dim.profile(AMSAAExactFail.nhpp.out,
                size = 5,
                save.s = T)
```

##	AMSAAWindow1

```{r amsaawindow1, eval=FALSE}
AMSAAWindow1.rdu <- frame.to.rdu(amsaawindow1,
                                 ID.column ="vehicle", 
                                 time.column ="miles", 
                                 event.column = "event")

attr(AMSAAWindow1.rdu,"WindowInfo")

event.plot(AMSAAWindow1.rdu)

RiskSet(AMSAAWindow1.rdu, JustEvent=F)
plotRiskSet(AMSAAWindow1.rdu)
plotRiskSet(AMSAAWindow1.rdu,proportion=T)

plot(mcf(AMSAAWindow1.rdu))

PlotMCFandNHPP(AMSAAWindow1.rdu,form = "log linear")

AMSAAWindow1.nhpp.out<-
  PlotMCFandNHPP(AMSAAWindow1.rdu,
                 form = "power rule")

one.dim.profile(AMSAAWindow1.nhpp.out,
                size = 5,
                save.s = T)
```

##	AMSAAWindow2

```{r amsaawindow2, eval=FALSE}
AMSAAWindow2.rdu <- frame.to.rdu(amsaawindow2,
                                 ID.column = "vehicle", 
                                 time.column = "miles" , 
                                 event.column = "event")

attr(AMSAAWindow2.rdu,"WindowInfo")

event.plot(AMSAAWindow2.rdu)

RiskSet(AMSAAWindow2.rdu)
RiskSet(AMSAAWindow2.rdu, JustEvent=F)
plotRiskSet(AMSAAWindow2.rdu)
plotRiskSet(AMSAAWindow2.rdu,proportion=T)
mcf(AMSAAWindow2.rdu)


plot(mcf(AMSAAWindow2.rdu))
```

## this was causing some crashes in R

```{r, eval=FALSE}
if(FALSE) {
PlotMCFandNHPP(AMSAAWindow2.rdu, form = "log linear")
AMSAAWindow2.nhpp.out <- 
  PlotMCFandNHPP(AMSAAWindow2.rdu,
                 form = "power rule")

one.dim.profile(AMSAAWindow2.nhpp.out,
                size = 5,
                save.s = T)

two.dim.profile(AMSAAWindow2.nhpp.out, 
                profile.on.list = NULL,
                which = c(1,2),
                size = c(5,5))

profile.contour(AMSAAWindow2.nhpp.outstruct1x2,
                transformationy = "log",
                variable.namey = "sigma", 
                variable.namex = "mu", 
                v = c(0.001, 0.01, .1,0.2, 0.4, 0.7, 0.9))

AMSAAWindow2.nhpp.loglin.out <- 
  PlotMCFandNHPP(AMSAAWindow2.rdu,
                 form = "log linear")

two.dim.profile(AMSAAWindow2.nhpp.loglin.out, 
                which = c(1,2), 
                size = c(9,9))

two.dim.profile(AMSAAWindow2.nhpp.loglin.out, 
                profile.on.list = NULL,
                which = c(1,2), 
                size = c(5,5), 
                range.list = list(c(1.6,2.4),c(.00010,.00016)))

profile.contour(AMSAAWindow2.nhpp.loglin.outstruct1x2,
                transformationy = "log",
                variable.namey = "sigma", 
                variable.namex = "mu",
                v = c(0.001, 0.01, .1,0.2, 0.4, 0.7, 0.9) )
}
```

##	Test

```{r, eval=FALSE}

if(F){
test.rdu <- frame.to.rdu(test,
	ID.column="Unit", time.column="Hours" ,event.column="Event",
	data.title = "Test Data", time.units =
	"Thousands of Hours of Operation")

summary(test.rdu)

event.plot(test.rdu)

event.plot(test.rdu)
print(mcf(test.rdu))
mcf.plot(test.rdu)
interarrival.times(test.rdu)

mcf.plot(test.rdu,
         xlab="Thousands of Hours of Operation",
         ylab="Cumulative Number of Maintenance Actions")

interarrival.plot(test.rdu,
                  xlab="Thousands of Hours of Operation",
                  ylab="Thousands of Hours Between Maintenance Actions",
                  my.title="")

ar1.plot(test.rdu,
         xlab="Lagged Thousands of Hours Between Maintenance Actions",
         ylab="Thousands of Hours Between Maintenance Actions")

ar1.plot(test.rdu,
	xlab="Lagged Thousands of Hours Between Maintenance Actions",
	ylab="Thousands of Hours Between Maintenance Actions",plot.acf=T)

fit.power.and.loglin.process(test.rdu,
                             xlab="Thousands of Hours of Operation",
                             ylab="Cumulative Number of Maintenance Actions") 
legend(1.55474, 
       63.7603,
       legend = c("Nonparametric MCF estimate",
                  "Log-linear Recurrence Rate NHPP MCF",
                  "Power Recurrence Rate NHPP MCF"),
       lty = c(1,1,3),
       lwd = c(3,1,1))


repair.tsplot(test.rdu)
interarrival.plot(test.rdu)
ar1.plot(test.rdu)

renewal.plots(test.rdu)
laplace.test(test.rdu)
lewis.robinson.test(test.rdu)
milhbk189.test(test.rdu)
dump(c("loglikeNHPP",
       "TestLike",
       "Sxloglikenhpp",
       "flogrecurrate",
       "fmcfdiff",
       "flogrecurratepower",
       "flogrecurrateloglin",
       "fmcf",
       "fmcfpower",
       "fmcfloglin"),"nhpp.q")
}
```
