---
title: "`r SMRD:::info('book')`"
subtitle: "`r SMRD:::info('chapter10')`"
author: "`r SMRD:::info('authors')`"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    css: my-vignette.css
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{echapter10}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
SMRD:::vinny()
library(SMRD)
```

# In This Vignette...


# Get Planning Values by Specifying a Point and a Slope

Specify a slope value and a single point $t, F(t)$

```{r}
plan.values1 <- get.plan.values("Weibull", 
                                beta = 2, 
                                prob = .1, 
                                time = 100, 
                                time.units = "Hours")
```


```{r}
summary(plan.values1)

plot(plan.values1)
failure.probabilities(plan.values1)
```

Carry out life test simulation using specified planning values.  The function below plots several individual test simulations (the number of simulations is equal to `number.detail`) along with a plot of several simulations depending on the value of the argument `number.sim` (default is 2000).

```{r}
life.test.simulation(plan.values1, 
                     n = 50,
                     censor.time = 120, 
                     number.detail = 5, 
                     quantile.mark = 0.2)
```

## Try a longer test

```{r}
life.test.simulation(plan.values1, 
                     n = 50,
                     censor.time = 300, 
                     number.detail = 5)
```

Other optional arguments and skip detail

```{r}
life.test.simulation(plan.values1, n=50,censor.time = 1000, number.sim = 50, quantile.mark=.2)
```

#now try lognormal distribution

influid.plan.values2 <- get.plan.values("Lognormal", sigma=.5,prob=.1, time=100, time.units="Hours")

summary(influid.plan.values2)
plot(influid.plan.values2)

plot(influid.plan.values2, censor.time=1000, grids=F)

life.test.simulation(influid.plan.values2, n=50,censor.time = 1000, quantile.mark=.1)

# Get planning values by specifying two points

influid.plan.values3 <- get.plan.values("Weibull",prob=c(.2,.12), time=c(1000,500), time.units="Hours")
influid.plan.values4 <- get.plan.values("Weibull",prob=c(.05,.15), time=c(40000,100000), time.units="Hours")

summary(influid.plan.values3)
plot(influid.plan.values3)


life.test.simulation(influid.plan.values3, n=50, censor.time = 1000, quantile.mark.1)

#compare the simulated value with the large-sample approx below

asd.quant(influid.plan.values3, n=50, censor.time = 1000, quantile.mark=.1)

#compare:

asd.quant(influid.plan.values3,n=50, censor.time = 1000, quantile.mark=.1)*sqrt(50)
asd.quant(influid.plan.values3,n=500, censor.time = 1000, quantile.mark=.1)*sqrt(500)
asd.quant(influid.plan.values3,n=5000, censor.time = 1000, quantile.mark=.1)*sqrt(5000)

#get a single variance factor like in Figures 10.5 and 10.6

variance.factor(distribution = 'normal', type = 'quantile', .02,.2)

#and for the normal distribution

variance.factor(distribution = 'sev',type = 'quantile', .02,.2)

asym.test.plan.properties(influid.plan.values3, n=50, proportion.failing=.1)

asd.quant(influid.plan.values3,n=50, censor.time = 1000, quantile.mark=c(0.1, 0.3, 0.5, 0.63))

#scaled fisher information matrix elements from the Escobar & Meeker algorithm:

lsinf(seq(-1,1,by=.1),"right","sev")

lsinf(seq(-2,2,by=.2),"right","normal")

# information like that in Table C.20

table.lines(seq(-1,1,by=.1),"sev")

table.lines(seq(-1,1,by=.1),"normal")


variance.factor("sev", type = 'quantile')
variance.factor("normal", type = 'quantile')
variance.factor("logistic", type = 'quantile')


variance.factor("sev", type = 'hazard')
variance.factor("normal", type = 'hazard')
variance.factor("logistic", type = 'hazard')

#number of test time.units needed for minimum-sized demonstration

zero.failure.plan(xrange=c(1.51,3.99), yrange=c(.1,29), krange=c(1.5,3.83))

zero.failure.plan(betavec = c( 1., 2.), quantile = 0.01, conlev = 0.95, xrange=c(1.51,10), yrange=c(.1,199), krange=c(1.5,10),grid=T,bw=FALSE)

#determine test length (multiple of spec)

zero.failure.k(beta = 2, quantile = 0.1, conlev = 0.99,	n = 5)

zero.failure.k(beta = 1, quantile = 0.01, conlev = 0.95, n = 5)

zero.failure.k(beta = 2, quantile = 0.01, conlev = 0.95, n = 5)

#determine sample size for a 0-failure test

zero.failure.n(conlev=.95, quantile=0.01, k=14, beta=1)

zero.failure.n(conlev=.95, quantile=0.01, k=3.369, beta=2)

zero.failure.prsd(alpha.vec=c(0.05,0.1),quantile=.01,pfactor=3)


#plan for a light bulb test

bulb.plan.values1 <- get.plan.values("normal", sigma=85, prob=.5, time=1000, time.units="Hours")

summary(bulb.plan.values1)
plot(bulb.plan.values1)

life.test.simulation(bulb.plan.values1, n=50,censor.time = 1000, number.detail=5, quantile.mark=.5)


plot(influid.plan.values3,censor.time=100,quantile.of.interest=.1)

#here is an example using type 2 censoring

plot(influid.plan.values3,fraction.failing=.1,quantile.of.interest=.1)

#in actual application, use number.sim = 10000 to get smoother curves


asym.sample.size(influid.plan.values3,censor.time=500,Rvalue=1.5,quantile.of.interest=.1)

asym.sample.size(influid.plan.values3,fraction.failing=.1,Rvalue=1.5,quantile.of.interest=.1)

asym.sample.size(bulb.plan.values1 ,fraction.failing=.1,HalfWidth=50,quantile.of.interest=.1)

mstt1.out <- multiple.simulate.type.two(n=c(20,30,40), r=c(20,30,40), distribution="lognormal", number.sim = 1000)


plot(mstt1.out,qprob=.9)

plot(mstt1.out,qprob=.8)

plot(mstt1.out,qprob=.5)


mstt2.out <- multiple.simulate.type.two(n=c(20,30,40), r=c(10,15,20), distribution="lognormal", number.sim = 1000)

plot(mstt2.out,qprob=.9)
plot(mstt2.out,qprob=.8)
plot(mstt2.out,qprob=.5,grids=T)

plot(multiple.simulate.type.two(n=c(24,28,33), r=c(24,28,33), distribution="normal", number.sim = 1000),qprob=.9)

# The following are for testing only and actual simulations should use at least 2000 trials

plot.prob.cs.type2("lognormal", k=2,n=c(5,10,20),r=c(3,6,12), number.sim=100)

plot.prob.cs.type2("loglogistic", k=2,n=c(5,10,20),r=c(3,6,12), number.sim=100)

plot.prob.cs.type2("weibull", k=2,n=c(5,10,20),r=c(3,6,12), number.sim=100)

plot.prob.cs.type2("frechet", k=2,n=c(5,10,20),r=c(3,6,12), number.sim=100)


