---
title: "`r SMRD2:::info('book')`"
subtitle: "`r SMRD2:::info('chapter10')`"
author: "`r SMRD2:::info('authors')`"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    css: my-vignette.css
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{echapter10}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
SMRD2:::vinny()
library(SMRD2)
```

# In This Vignette...


# Get Planning Values by Specifying a Point and a Slope

Specify a slope value and a single point $t, F(t)$

```{r}
plan.values1 <- get.plan.values("Weibull", 
                                beta = 2, 
                                prob = .1, 
                                time = 100, 
                                time.units = "Hours")
```


```{r}
summary(plan.values1)

plot(plan.values1)
failure.probabilities(plan.values1)
```

Carry out life test simulation using specified planning values.  The function below plots several individual test simulations (the number of simulations is equal to `number.detail`) along with a plot of several simulations depending on the value of the argument `number.sim` (default is 2000).

```{r}
life.test.simulation(plan.values1, 
                     n = 50,
                     censor.time = 120, 
                     number.detail = 5, 
                     quantile.mark = 0.2)
```

## Try a longer test

```{r}
life.test.simulation(plan.values1, 
                     n = 50,
                     censor.time = 300, 
                     number.detail = 5)
```

Other optional arguments and skip detail

```{r}
life.test.simulation(plan.values1, 
                     n = 50,
                     censor.time = 1000, 
                     number.sim = 50, 
                     quantile.mark = 0.2)
```

Now try lognormal distribution

```{r}
plan.values2 <- get.plan.values("Lognormal", 
                                sigma = 0.5,
                                prob = 0.1, 
                                time = 100, 
                                time.units = "Hours")

summary(plan.values2)
plot(plan.values2)

plot(plan.values2, 
     censor.time = 1000, 
     grids = F)

life.test.simulation(plan.values2, 
                     n = 50,
                     censor.time = 1000, 
                     quantile.mark = .1)
```

# Get planning values by specifying two points

```{r}
plan.values3 <- get.plan.values("Weibull",
                                prob = c(.2,.12),
                                time = c(1000,500), 
                                time.units = "Hours")

plan.values4 <- get.plan.values("Weibull",
                                prob = c(.05,.15),
                                time = c(40000,100000),
                                time.units = "Hours")

summary(plan.values3)
plot(plan.values3)


life.test.simulation(plan.values3, 
                     n = 50, 
                     censor.time = 1000, 
                     quantile.mark = 0.1)

#compare the simulated value with the large-sample approx below

asd.quant(plan.values3, 
          n=50, 
          censor.time = 1000, 
          quantile.mark=.1)

#compare:

asd.quant(plan.values3,
          n=50, 
          censor.time = 1000, 
          quantile.mark=.1)*sqrt(50)

asd.quant(plan.values3,
          n=500, 
          censor.time = 1000, 
          quantile.mark=.1)*sqrt(500)

asd.quant(plan.values3,
          n=5000, 
          censor.time = 1000, 
          quantile.mark=.1)*sqrt(5000)
```

#get a single variance factor like in Figures 10.5 and 10.6

```{r}
# For the normal distribution
variance.factor(distribution = 'normal', 
                type = 'quantile', 
                quantile.of.interest = 0.02,
                proportion.failing = 0.2)


# For the smallest extreme value distribution
variance.factor(distribution = 'sev',
                type = 'quantile', 
                quantile.of.interest = 0.02,
                proportion.failing = 0.2)
```

```{r}
asym.test.plan.properties(plan.values3, 
                          n = 50, 
                          proportion.failing = 0.1)

asd.quant(plan.values3,
          n = 50, 
          censor.time = 1000, 
          quantile.mark = c(0.1, 0.3, 0.5, 0.63))
```

Scaled fisher information matrix elements from the Escobar & Meeker algorithm

```{r}
lsinf(seq(-1,1, by = 0.1),"right","sev")

lsinf(seq(-2,2, by = 0.2),"right","normal")
```

Generate information table like that shown in Table C.20

```{r}
table.lines(seq(-1,1,by=.1),"sev")

table.lines(seq(-1,1,by=.1),"normal")
```

```{r}
variance.factor("sev", type = 'quantile')
variance.factor("normal", type = 'quantile')
variance.factor("logistic", type = 'quantile')


variance.factor("sev", type = 'hazard')
variance.factor("normal", type = 'hazard')
variance.factor("logistic", type = 'hazard')
```

Number of test time units needed for minimum-sized demonstration

```{r}
zero.failure.plan(xlim = c(1.51,3.99), 
                  ylim = c(.1,29), 
                  krange = c(1.5,3.83))

zero.failure.plan(betavec = c( 1., 2.), 
                  quantile = 0.01, 
                  conlev = 0.95, 
                  xlim = c(1.51,10), 
                  ylim = c(.1,199), 
                  krange = c(1.5,10),
                  grid = T,
                  bw = FALSE)
```

Determine test length (multiple of spec)

```{r}
zero.failure.k(beta = 2, quantile = 0.1, conlev = 0.99,	n = 5)

zero.failure.k(beta = 1, quantile = 0.01, conlev = 0.95, n = 5)

zero.failure.k(beta = 2, quantile = 0.01, conlev = 0.95, n = 5)
```

Determine sample size for a 0-failure test

```{r}
zero.failure.n(conlev = 0.95, quantile = 0.01, k = 14, beta = 1)

zero.failure.n(conlev = 0.95, quantile = 0.01, k = 3.369, beta = 2)

zero.failure.prsd(alpha.vec = c(0.05,0.1), quantile = 0.01, pfactor = 3)
```

# Plan for a light bulb test

```{r}
bulb.plan.values1 <- get.plan.values("normal", 
                                     sigma = 85, 
                                     prob = 0.5,
                                     time = 1000,
                                     time.units = "Hours")

summary(bulb.plan.values1)
plot(bulb.plan.values1)

life.test.simulation(bulb.plan.values1, 
                     n = 50,
                     censor.time = 1000, 
                     number.detail = 5,
                     quantile.mark = 0.5)
```

```{r}
plot(plan.values3,
     censor.time = 100,
     quantile.of.interest = 0.1)

#here is an example using type 2 censoring

plot(plan.values3,
     fraction.failing = 0.1,
     quantile.of.interest = 0.1)

# In actual application, use number.sim = 10000 to get smoother curves

asym.sample.size(plan.values3,
                 censor.time = 500,
                 Rvalue = 1.5,
                 quantile.of.interest = 0.1)

asym.sample.size(plan.values3,
                 fraction.failing = 0.1,
                 Rvalue = 1.5,
                 quantile.of.interest = 0.1)

asym.sample.size(bulb.plan.values1,
                 fraction.failing = 0.1,
                 HalfWidth = 50,
                 quantile.of.interest = 0.1)
```

```{r}
mstt1 <- multiple.simulate.type.two(n = c(20,30,40), 
                                    r = c(20,30,40),
                                    distribution = "lognormal",
                                    number.sim = 1000)

plot(mstt1, qprob = 0.9)
plot(mstt1, qprob = 0.8)
plot(mstt1, qprob = 0.5)


mstt2 <- multiple.simulate.type.two(n = c(20,30,40), 
                                    r = c(10,15,20),
                                    distribution = "lognormal",
                                    number.sim = 1000)

plot(mstt2, qprob = 0.9)
plot(mstt2, qprob = 0.8)
plot(mstt2, qprob = 0.5, grids = T)

mstt3 <- multiple.simulate.type.two(n = c(24,28,33), 
                                    r = c(24,28,33),
                                    distribution = "normal", 
                                    number.sim = 1000)

plot(mstt3, qprob = 0.9)
```

The following are for testing only and actual simulations should use at least 2000 trials

```{r}
plot.prob.cs.type2("lognormal", 
                   k = 2,
                   n = c(5,10,20),
                   r = c(3,6,12), 
                   number.sim = 100)

plot.prob.cs.type2("loglogistic", 
                   k = 2,
                   n = c(5,10,20),
                   r = c(3,6,12), 
                   number.sim = 100)

plot.prob.cs.type2("weibull", 
                   k = 2,
                   n = c(5,10,20),
                   r = c(3,6,12), 
                   number.sim = 100)

plot.prob.cs.type2("frechet", 
                   k = 2,
                   n = c(5,10,20),
                   r = c(3,6,12),
                   number.sim = 100)
```