---
title: "`r SMRD:::info('book')`"
subtitle: "`r SMRD:::info('chapter1')`"
author: "`r SMRD:::info('authors')`"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    css: my-vignette.css
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{echapter1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
SMRD:::vinny()
library(SMRD)
```

# In This Vignette...

An overview of `life.data` objects

- Creating `life.data` objects with `frame.to.ld()`

- Viewing and subsetting elements

- Plotting `life.data` objects

# Leiblien-Zelen Data Set `lzbearing`

Overview of the data set 

- Complete data set 23 observations 
Most basic

```{r}
DT::datatable(lzbearing, options = list(pageLength = 8))
```



- Many functions in the SMRD package require a `life.data` object.  `life.data` objects are created using the function `frame.to.ld`.

```{r}
lzbearing.ld <- frame.to.ld(lzbearing, 
                            response.column = 1,
                            time.units = "Megacycles")
```

- Once the `life.data` has been created, several plots and values can be produced

```{r}
event.plot(lzbearing.ld)

summary(lzbearing.ld)

print(lzbearing.ld)

plot(lzbearing.ld,
     band.type = "none")
```

## Nelson's Super-Alloy Data Set `superalloy`

```{r}
superalloy.ld <- frame.to.ld(superalloy,
                             response.column = 1, 
                             censor.column = 2,
                             x.columns = c(5,6,4),
                             time.units = "Kilocycles")



summary(superalloy.ld)

censored.data.plot(superalloy.ld, 
                   explan.var = 3)

censored.data.plot(superalloy.ld, 
                   explan.var = 3,
                   response.on.yaxis = F)


censored.data.plot(superalloy.ld, 
                   explan.var = 3, 
                   x.axis = "log", 
                   y.axis = "log")

censored.data.plot(superalloy.ld, 
                   explan.var = 3,
                   response.on.yaxis = F, 
                   x.axis = "log", 
                   y.axis = "log")
```