---
title: "`r SMRD:::info('book')`"
subtitle: "`r SMRD:::info('chapter1')`"
author: "`r SMRD:::info('authors')`"
date: "`r Sys.Date()`"
output: 
  html_document:
    css: smrd.css
    fig_caption: yes
---

```{r, echo=FALSE}
SMRD:::vinny()
library(SMRD)
```

# In This echapter...

An overview of the `SMRD` package features

An overview of working with `life.data` objects

- Creating `life.data` objects with `frame.to.ld()`

- Viewing and subsetting elements

- Plotting `life.data` objects

## `SMRD` Package Features 

SMRD is designed to easily return estimation/prediction results for many types of failure data

- Multiple failure events
- Censored data (right, left, and interval censoring)
- Truncated data (right, left, and interval truncation)
- Failure data with explanatory variables (failure-time regression)
- Repeated measures degradation data (linear & non-linear mixed effects)
- Repairable system failure data (recurring events)
- Physical/performance degradation data
- Failure data with prior information (Bayesian reliability)
- Reliability growth test data
- Reliability test simulations

`SMRD` facilitates minimal data pre-processing through flexible event definitions

- Organizations often use different terms to describe the same event

    + 'Failure' = 'Failed' = 'Fail' = 'dead' = 'died'</li>
    + 'right' = 'rcensored' = 'suspended' = 'alive'
    + 'left' = 'doa' = 'lcensored'
    + 'interval' = 'int' = 'icensored' = 'grouped'

- Many applications use ambiguous numerical codes to represent these events

    + Often, the numerical event codes used by one software package don't coincide with those used by other packages
    + `SMRD` allows for flexible event definitions to utilize the data as-is
    + <focus>Event definitions can even be mixed</focus>
    + `SMRD` event definitions easily mapped to `survival` numeric definitions

The table below shows the default `SMRD` default event definitions

```{r}
fail <- strsplit(SMRDOptionsDefaults()$SMRD.F,  split = ',')[[1]]
left <- strsplit(SMRDOptionsDefaults()$SMRD.Lc, split = ',')[[1]]
righ <- strsplit(SMRDOptionsDefaults()$SMRD.Rc, split = ',')[[1]]
intv <- strsplit(SMRDOptionsDefaults()$SMRD.Ic, split = ',')[[1]]
lengths <- lapply(X = list(fail,left,righ,intv), 
                  FUN = function(x) length(x))

Length <- max(unlist(lengths))

fails <- c(fail, rep('', Length-length(fail)))
lefts <- c(left, rep('', Length-length(left)))
righs <- c(righ, rep('', Length-length(righ)))
intvs <- c(intv, rep('', Length-length(intv)))
dats <- data.frame(fails,lefts,righs,intvs)
colnames(dats) <- c('Failed', 
                    'Left-censored',
                    'Right-censored',
                    'Interval-censored') 
DT::datatable(dats, options = list(pageLength = 20))
```

`SMRD` includes over 100 datasets

- Many of these data sets still need to be documented

- A list of these data sets is returned using `data(package = "SMRD")`

- Likewise, the names and descriptions of the data sets is shown in the table below

```{r}
DT::datatable(as.data.frame(data(package = 'SMRD')$results[,c(-2)]))
```

# Analyzing the Leiblien-Zelen Data Set `lzbearing`

Overview of the data set 

- Complete data set 23 observations
- Most basic of the data sets included in the package

```{r}
DT::datatable(lzbearing, options = list(pageLength = 8))
```

- Many functions in the SMRD package require a `life.data` object.  `life.data` objects are created using the function `frame.to.ld`.

```{r}
lzbearing.ld <- frame.to.ld(lzbearing, 
                            response.column = 1,
                            time.units = "Megacycles")
```

- Once the `life.data` has been created, several plots and values can be produced

```{r}
event.plot(lzbearing.ld)

summary(lzbearing.ld)

print(lzbearing.ld)

plot(lzbearing.ld, distribution = "weibull")
```

Many other plots and numerical results can also be easily returned as shown in the next example

- Plots

    + Nonparametric CDF plots 
    + Parametric CDF plots
    + ML CDF and hazard plots
    + Explanatory variable plots
    + Multi-failure mode plots
    + Relative likelihood surfaces
    + Relative likelihood curves

- Numerical results 

    + $F(t)$ at specified values of $t$
    + $h(t)$ at specified values of $t$
    + $t^{-1}(p)$ at specified values of $p$
    + ML parameter estimates and standard errors
    + Logit and log transformed confidence intervals (pointwise and simultaneous)

# Example: Analyzing the `shockabsorber` dataset

## Dataset: `shockabsorber`

- This example demonstrates some of the `SMRD` functions to analyze the shockabsorber dataset used throughout the text

```{r, comment=NA}
shockabsorber
```

- Creating the `life.data` object

```{r, echo=TRUE}
shock.ld <- frame.to.ld(frame = shockabsorber,
                        response.column = 1,
                        failure.mode.column = 2,
                        censor.column = 3,
                        time.units = 'Kilometers')
```

- Nonparametric & Parametric CDF plots

```{r, echo=-1, fig.align='center', fig.width=10}
par(mfrow = c(1,2), bg = NA)
plot(shock.ld)
plot(shock.ld, distribution = 'lognormal')
```

- Maximum likelihood plots $F(t)$ \& $h(t)$

```{r, echo=-1, fig.width=10, fig.align='center'}
par(mfrow = c(1,2), bg = NA)
mlehazplot(shock.ld,  distribution = 'lognormal', param.loc = 'topleft')
mleprobplot(shock.ld, distribution = 'weibull', param.loc = 'topleft')
```

- Relative likelihood surface plots

```{r, echo=-1, fig.width=10, fig.align='center'}
par(mfrow = c(1,2), bg = NA, las = 1)
simple.contour(shock.ld, distribution = 'sev', threeD = T, original.par = F)
simple.contour(shock.ld, distribution = 'sev', show.confidence = F, zoom = 1.75)
```

- Maximum likelihood estimate results

```{r, echo=TRUE}
(print(mlest(shock.ld, distribution = 'weibull')))
```

# Example: Nelson's Super-Alloy Data Set `superalloy`

```{r}
superalloy.ld <- frame.to.ld(superalloy,
                             response.column = 1, 
                             censor.column = 2,
                             x.columns = c(5,6,4),
                             time.units = "Kilocycles")

summary(superalloy.ld)

censored.data.plot(superalloy.ld, 
                   explan.var = 1)

censored.data.plot(superalloy.ld, 
                   explan.var = 3,
                   response.on.yaxis = F)

censored.data.plot(superalloy.ld, 
                   explan.var = 3, 
                   x.axis = "log", 
                   y.axis = "log")

censored.data.plot(superalloy.ld, 
                   explan.var = 3,
                   response.on.yaxis = F, 
                   x.axis = "log", 
                   y.axis = "log")
```